Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-06-27 pirouette_supplement.tex
Moved 'acknowledgements', 'data accessibility' and 'author contribitions' to supplementary materials. 2967 words

\begin{itemize}
  \item{
    subsection \ref{subsec:guidelines}: guidelines for users
  }
  \item{
    subsection \ref{subsec:installation}: installation
  }
  \item{
    subsection \ref{subsec:resources}: resources, such as 
    website, tutorials, packages used, bug reporting and contributing
  }
  \item{
    subsection \ref{subsec:citation}: citation of pirouette
  }
  \item{
    subsection \ref{subsec:twinning_mathematics}: the mathematics of the
    twinning process
  }
  \item{
    subsection \ref{subsec:main_functions}: main functions
  }
  \item{
    subsection \ref{subsec:main_example}: code, extra figures and
    diagnostics regarding the main example.
  }
  \item{
    subsection \ref{subsec:distribution}: the result of using 
    multiple trees, as generated by the
    same stochastic process as the main example
  }
  \item{
    subsection \ref{subsec:n_taxa}: the effect of the number
    of taxa
  }
  \item{
    subsection \ref{subsec:n_nucleotides}: the effect of the DNA
    alignment sequence length
  }
  \item{
    subsection \ref{subsec:simplest_correct_parameterization} shows the
    effect when doing an inference in the simplest use case
  }
  \item{
    subsection \ref{subsec:under_parameterization} shows the
    effect when doing an inference with an under-parameterization
  }
  \item{
    subsection \ref{subsec:different_n_mutations} shows the
    effect when the twin alignment is allowed to have a different
    number of \new{substitution}s
  }
  \item{
    subsection \ref{subsec:mutation_rate} shows the
    effect of different mutation rates
  }
\end{itemize}

@@

>>>>

\begin{itemize}
  \item{
    subsection \ref{subsec:guidelines}: guidelines for users
  }
  \item{
    subsection \ref{subsec:installation}: installation
  }
  \item{
    subsection \ref{subsec:resources}: resources, such as 
    website, tutorials, packages used, bug reporting and contributing
  }
  \item{
    subsection \ref{subsec:citation}: citation of pirouette
  }
  \item{
    subsection \ref{subsec:twinning_mathematics}: the mathematics of the
    twinning process
  }
  \item{
    subsection \ref{subsec:main_functions}: main functions
  }
  \item{
    subsection \ref{subsec:main_example}: code, extra figures and
    diagnostics regarding the main example.
  }
  \item{
    subsection \ref{subsec:distribution}: the result of using 
    multiple trees, as generated by the
    same stochastic process as the main example
  }
  \item{
    subsection \ref{subsec:n_taxa}: the effect of the number
    of taxa
  }
  \item{
    subsection \ref{subsec:n_nucleotides}: the effect of the DNA
    alignment sequence length
  }
  \item{
    subsection \ref{subsec:simplest_correct_parameterization} shows the
    effect when doing an inference in the simplest use case
  }
  \item{
    subsection \ref{subsec:under_parameterization} shows the
    effect when doing an inference with an under-parameterization
  }
  \item{
    subsection \ref{subsec:different_n_mutations} shows the
    effect when the twin alignment is allowed to have a different
    number of \new{substitution}s
  }
  \item{
    subsection \ref{subsec:mutation_rate} shows the
    effect of different mutation rates
  }
  \item{
    subsection \ref{subsec:acknowledgments}: Acknowledgments
  }
  \section{
    subsection \ref{subsec:data_accessibility}: Data accessibility
  }
  \section{
    subsection \ref{subsec:author_contributions}: Author contributions
  }
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
\label{subsec:acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We thank the Center for Information Technology of the University 
of Groningen for its support and for providing access to the Peregrine 
high performance computing cluster. 
We thank the Netherlands 
Organization for Scientific Research (NWO) for financial support 
through a VICI grant awarded to RSE.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data accessibility}
\label{subsec:data_accessibility}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

All code is archived at 
\url{http://github.com/richelbilderbeek/pirouette_article},
with DOI \url{https://doi.org/12.3456/zenodo.1234567}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Author contributions}
\label{subsec:author_contributions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

RJCB, GL and RSE conceived the idea for the package. 
RJCB created, tested and revised the package.
GL provided major contributions to the package.
RJCB wrote the first draft of the manuscript, 
GL and RSE contributed to revisions.
